Holomorphic field theories and higher algebra

### 2024-09-27 draft.tex
just looking at changes

In physics, the relationship between the Weyl algebra on generators $p,q$ and its loopy version $W[V]$ is through a process called `dimensional reduction'.
The key idea is that to any quantum mechanical system there is an algebra of operators---the loopy version of the Weyl algebra arises from a quantum mechanical system on the infinite-dimensional space of loops in the symplectic vector space $V$. 
We will unpack this statement in the language of fields and Lagrangians.

@@

We can extract from $L_{2d}$ a Lagrangian on a one-dimensional space by the process of `compactification'. 
It is natural to take as this one-dimensional space the radial direction in $\CC^\times$.
Then, compactification involves integrating out the remaining circle direction.
Concretely, any smooth function on $\CC^\times$ can be decomposed in polar coordinates as
\[
\phi(r,\theta) = \sum_{k \in \ZZ} \phi_k(r) e^{2 \pi i k \theta} ,
\]
where $\phi_k(r)$ is a smooth function depending only on the radius $r \in \RR_+$.
Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the `time' parameter $t = \log r \in \RR$. 
We interpret $\sum_{k \in \ZZ} \phi_k(r)$ as smooth map from $\RR$ to the formal loop space $LV$.

At the level of Lagrangians we can integrate $L_{2d}(\phi)$ over $S^1$ to obtain the following infinite sum of one-dimensional Lagrangians
\beqn
L_{1d}(\phi_k, k \in \ZZ) = \sum_{k\in \ZZ} \phi_{-k} \d \phi_{k} + k \phi_k \phi_{-k} \d t .
\eeqn 
Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
In general, we find mechanics into the symplectic vector space $LV$, where the symplectic structure uses the residue pairing in addition to the symplectic form on $V$, with a nontrivial Hamiltonian that encodes the $U(1)$-symmetry arising from rotating $LV$ in the natural way.

@@

\owen{Improve!}
An algebra $A$ over this cooperad means that for each radius~$r$, 
there is a dg vector space $A(r)$, and for any list of radii $r_1,\ldots, r_n, R$,
there is a cochain map
\[
\alpha(r_1, \ldots, r_n| R): A(r_1) \otimes \cdots \otimes A(r_n) \to A(R) \otimes \Omega^{0,\bu}(\PDisc_d(r_1, \ldots, r_n| R)) .
\]
To invest the map $\alpha$ with more meaning, 
pick a real, closed submanifold $T \subset \PDisc_d(r_1, \ldots, r_n| R)$, along which one can integrate $(0,k)$-forms.
For instance, for any inputs $a_i \in A(r_i)$, we get an element in $A(R)$~by
\[
\int_T \alpha(a_1 \otimes \cdots \otimes a_n),
\]
where we have suppressed distracting notation from~$\alpha$.

@@

The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
\[
{\rm Map}(X , \left( \fg_\CC^*\times {\rm Crit}^d(W) \right)/ G_\CC), 
\]
where the target is a derived quotient stack whose first factor arises from the BF theory and whose second factor arises from the matter multiplet.

@@

There will be two holomorphic theories on $\CC^2$. 
We call one side {\em electric} and the other {\em magnetic}.
These turn out to be the twists of the original electric and magnetic supersymmetric theories of the famous Seiberg duality, which justifies our terminology.

@@

\begin{conj}[\cite{Eager}]
Let $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
Construct a quantization of the theories $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$.
There is an equivalence of 2-dimensional holomorphic factorization algebras
\[
\Obs_{\sfE} \simeq \Obs_{\sfM}  
\]
where these are the observables of the electric and magnetic theories, respectively.
\end{conj}

>>>>

In physics, the relationship between the Weyl algebra on generators $p, q$ and its loopy version $W[V]$ is by a process called {\it dimensional reduction}.
The key idea is that to any quantum mechanical system there is an algebra of operators---the loopy version of the Weyl algebra arises from a quantum mechanical system on the infinite-dimensional space of loops in the symplectic vector space $V$. 
We will unpack this statement in the language of fields and Lagrangians.

@@

We can extract from $L_{2d}$ a Lagrangian on a one-dimensional space by the process of {\it compactification}. 
It is natural to take as this one-dimensional space the radial direction in $\CC^\times$.
Then, compactification involves integrating out the remaining circle direction.
Concretely, any smooth function on $\CC^\times$ can be decomposed in polar coordinates as
\[
\phi(r,\theta) = \sum_{k \in \ZZ} \phi_k(r) e^{2 \pi i k \theta} ,
\]
where $\phi_k(r)$ is a smooth function depending only on the radius $r \in \RR_+$.
Alternatively, by taking the logarithm we can view $\phi_k(t)$ as a function of the `time' parameter $t = \log r \in \RR$. 
We interpret $\sum_{k \in \ZZ} \phi_k(r)$ as smooth map from $\RR$ to the formal loop space $LV$.

At the level of Lagrangians we can integrate $L_{2d}(\phi)$ over $S^1$ to obtain the following infinite sum of one-dimensional Lagrangians
\beqn
L_{1d}\left( \ldots, \phi_{-1}, \phi_0 , \phi_1, \ldots \right) = \sum_{k\in \ZZ} \phi_{-k} \,\d \phi_{k} + k\, \phi_k \, \phi_{-k} \, \d t .
\eeqn 
Notice that the $k=0$ summand is just the Lagrangian of ordinary mechanics into $V$ with zero Hamiltonian. 
In general, we find mechanics into the symplectic vector space $LV$, where the symplectic structure uses the residue pairing in addition to the symplectic form on $V$, with a nontrivial Hamiltonian that encodes the $U(1)$-symmetry arising from rotating $LV$ in the natural way.

@@

\owen{Improve!}
An algebra $A$ over this cooperad means that for each radius~$r$, 
there is a dg vector space $A(r)$, and for any list of radii $r_1,\ldots, r_n, R$,
there is a cochain map
\[
\alpha(r_1, \ldots, r_n| R): A(r_1) \otimes \cdots \otimes A(r_n) \to A(R) \otimes \Omega^{0,\bu}(\PDisc_d(r_1, \ldots, r_n| R)) .
\]
To invest the map $\alpha$ with more meaning, 
pick a real, closed submanifold 
\[
T \subset \PDisc_d(r_1, \ldots, r_n| R)
\]
along which one can integrate $(0,k)$-forms.
For instance, for any inputs $a_i \in A(r_i)$, we get an element in $A(R)$~by
\[
\int_T \alpha(a_1 \otimes \cdots \otimes a_n),
\]
where we have suppressed distracting notation from~$\alpha$.

@@

The holomorphic twist of a theory with both vector and matter multiplets then corresponds to the  derived mapping space
\[
{\rm Map}(X , [( \fg_\CC^*\times {\rm Crit}^d(W))/ G_\CC]), 
\]
where the target is a derived quotient stack whose first factor arises from the BF theory and whose second factor arises from the matter multiplet.

@@

There will be two holomorphic theories on $\CC^2$. 
We call one side {\em electric} and the other {\em magnetic}.
These turn out to be the twists of the original electric and magnetic supersymmetric theories of the famous Seiberg duality, 
which motivates our terminology.

@@

\begin{conj*}[\cite{Eager}]
Let $F = N + \check{N}$ and $F \geq N, \check{N} \geq 2$.
Construct a quantization of the theories $\cT_{\sfE}(F,N)$ and $\cT_{\sfM}(F,\check{N})$.
There is an equivalence of 2-dimensional holomorphic factorization algebras
\[
\Obs_{\sfE} \simeq \Obs_{\sfM}  
\]
where these are the observables of the electric and magnetic theories, respectively.
\end{conj*}
